Demography and linked selection in wild and domesticated maize

### 2015-08-14 manuscript.tex
pi plots

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/SFS_and_Tajima.png}
\caption{The folded SFS and Tajimas D were calculated both inside and outside of genes for maize and teosinte. In both taxa, a dearth of rare alleles was observed within genes relative to outside of genes, which led to higher values of Tajima's D outside of genes than inside.{\bf A:} Folded SFS for maize; {\bf B:} Folded SFS for teosinte; {\bf C:} Maize Tajima's D; {\bf D:} Teosinte Tajima's D.  \label{fig:diversity} \jri{skip the SFS and make this a panel plot of pi and TajD in maize and teosinte} } 
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/Pi_and_Tajima.png}
\caption{Pairwise diversity (Pi) and Tajimas D were calculated both inside and outside of genes for maize and teosinte. In both taxa, a dearth of rare alleles was observed within genes relative to outside of genes, which led to higher values of Tajima's D outside of genes than inside.{\bf A:} Histogram of Pi in 1 kb windows in maize; {\bf B:} Histogram of Pi in 1 kb windows in teosinte; {\bf C:} Histogram of Tajima's D in 1 kb windows in maize; {\bf D:} Histogram of Tajima's D in 1 kb windows in teosinte.  \label{fig:diversity} \jri{skip the SFS and make this a panel plot of pi and TajD in maize and teosinte} } 
\end{figure}
